---
title: "Case Study"
author: "Mari Sanders"
date: "2024-10-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(p8105.datasets)
library(leaflet)
```


```{r}
data("nyc_airbnb")

nyc_airbnb %>% view()
```


## Questions about Data

* Where are max and min airbnb prices? 

  * What are average prices? 
  
  * What factors affect prices? 

* Where are prices going up and down overtime? 

* What's the relationship bewteen number of reviews and average reviews? 

* Does room type affect availability? 

* What's the location of the unit? 

  * What areas are popular? 
  
  * How do we measure popularity? Population = number of units? Average Price?
  
* Are there repeat hosts?
  
  * If there are, what does that mean?
  

```{r}
nyc_airbnb %>% janitor::clean_names() %>%
  select(price, room_type, neighbourhood) %>%  
  ggplot(aes(x = room_type, y = price)) + 
  geom_boxplot()
```

```{r}
nyc_airbnb %>% 
  janitor::clean_names() %>% pull(price) %>% 
  mean()
```

```{r}
nyc_airbnb %>% 
  janitor::clean_names() %>% pull(price) %>% 
  min()
```

```{r}
nyc_airbnb %>% 
  janitor::clean_names() %>% pull(price) %>% 
  max()
```

```{r}
summary(nyc_airbnb)
```

```{r}
nyc_airbnb %>%  
  janitor::clean_names() %>% 
  select(price, room_type, neighbourhood) 
```


```{r}
ggplot(data = nyc_airbnb, aes(x = room_type, y = availability_365)) + 
  geom_violin()
```


```{r}
ggplot(data = nyc_airbnb, aes(x = number_of_reviews, y = review_scores_location, na.rm = TRUE)) + geom_point()
```

```{r}
nyc_airbnb %>% 
  filter(calculated_host_listings_count > 34) %>%  view()
```

```{r}
nyc_airbnb %>%  
  group_by(neighbourhood_group) %>% 
  summarise(total_reviews = sum(number_of_reviews, na.rm = TRUE)) %>% 
  arrange(desc(total_reviews))
```

```{r}
nyc_airbnb %>%  
  group_by(neighbourhood_group, room_type) %>% 
  summarize(mean_price = mean(price)) %>% 
  pivot_wider(
    names_from = room_type, 
    values_from = mean_price
  ) 
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = review_scores_location, y = price)) +
  geom_point()
```

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan", price < 1000) %>%  
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.1)
```

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan", price < 1000, room_type == "Entire home/apt") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price)) %>% arrange(desc(mean_price))
```

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan", price < 1000, room_type == "Entire home/apt") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) + 
  geom_violin() + 
  theme(axis.text = element_text(angle = 45, vjust = 1, hjust = 1))
```

**Go Back to Map**

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan", price < 1000) %>%  
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.1)
```

```{r}
pal <- colorNumeric(c("red", "green", "blue"), 1:1000)
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan", price < 1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, color = ~ pal(price), radius = 2) 
```


